Data preparation

### 2020-04-10 production/prod_prep-data-A.rmd
update-1004-2020

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prep-data-A.Rmd",output_format = "html_document",output_dir = ".")
```

@@

```{r}
dat04 <- w01 %>% filter(Intro==1) %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03_p"),
         starts_with("FL_21_DO"))
dat04$grupo <- NA
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)

dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
```

## Translation of variable labels and value labels.
```{r}
label(dat04$grupo) <- "This variable classifies the interviewees according to the order in which the indicators are shown within the scale. There are three orders  of items on the scale. In the first order (group 1), questions of the same factor are then presented to them, in the second order (group 2) they were separated and in the third order (group 3) at random."

dat04$perc_effort <- set_labels(dat04$perc_effort,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they manage to get bigger
rewards that those who strive
less."

dat04$perc_talent <- set_labels(dat04$perc_talent,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they manage to obtain
greater rewards than those who possess
less talent."

dat04$perc_wpart <- set_labels(dat04$perc_wpart,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have rich parents manage to get out
ahead."

dat04$perc_netw <- set_labels(dat04$perc_netw,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have good contacts they manage to get out
ahead."

dat04$pref_effort <- set_labels(dat04$pref_effort,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they should get
greater rewards than those who
they try less."

dat04$pref_talent <- set_labels(dat04$pref_talent,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they should get
greater rewards than those who possess
less talent."

dat04$pref_wpart <- set_labels(dat04$pref_wpart,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Is
well that those who have good
contacts get ahead."

dat04$pref_netw <- set_labels(dat04$pref_netw,  labels = c("strongly disagree", "disagreement", "Neither agree nor disagree","Agree", "totally agree"))
label(dat04$pref_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Is
well that those who have good
contacts get ahead."
```

@@

```{r}
dat01 <- dat04 %>% filter(grupo==1) %>%  na.omit()
```

@@

```{r}
dat03 <- dat04 %>% filter(grupo==3) %>%  na.omit()
```

@@

Add tags wave 1
```{r }
label(w01$Intro) <- "If you wish to participate, select the alternative I ACCEPT take part in this investigation. If you do not want to participate in this study, press the alternative I NOT ACCEPT take part in this investigation."

w01$Intro <- set_labels(w01$Intro,  labels = c("I ACCEPT take part in this investigation","I NOT ACCEPT take part in this investigation."))
```

@@

```{r}
w01c <- w01b
w01c$grupo <- NA
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
w01c$perc_effort_w1 <- rowSums(w01c[,c(matches(match = "perc_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_talent_w1 <- rowSums(w01c[,c(matches(match = "perc_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_wpart_w1  <- rowSums(w01c[,c(matches(match = "perc_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$perc_netw_w1   <- rowSums(w01c[,c(matches(match = "perc_netw"  ,vars = names(w01c)))],na.rm = TRUE)

w01c$pref_effort_w1 <- rowSums(w01c[,c(matches(match = "pref_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_talent_w1 <- rowSums(w01c[,c(matches(match = "pref_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_wpart_w1  <- rowSums(w01c[,c(matches(match = "pref_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_netw_w1   <- rowSums(w01c[,c(matches(match = "pref_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c[w01c==0] <- NA
w01c <- w01c %>% select(grupo,
                        perc_effort_w1,perc_talent_w1,perc_wpart_w1,perc_netw_w1,
                        pref_effort_w1,pref_talent_w1,pref_wpart_w1,pref_netw_w1,
                        sexo_w1=sexo,edad_w1=edad,edcep_w1=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w01c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

Add tags wave 2
```{r }
label(w02$Intro) <- "If you wish to participate, select the alternative I ACCEPT take part in this investigation. If you do not want to participate in this study, press the alternative I NOT ACCEPT take part in this investigation."

w02$Intro <- set_labels(w02$Intro,  labels = c("I ACCEPT take part in this investigation","I NOT ACCEPT take part in this investigation."))
```

@@

Delete those who do not accept and Delete those who do not accept
```{r}
w02b <- w02 %>% filter(Intro==1, Finished==1) %>% as.data.frame()
w02b$ID <- stringr::str_split_fixed(w02b$ticket, "_", 4)[,1]

```

@@

```{r}
w02c <- w02b

w02c$treat <- NA
w02c$treat[w02c$FL_6_DO_Control==1] <- 1
w02c$treat[w02c$FL_6_DO_Tratamiento==1] <- 2
w02c$treat[w02c$FL_6_DO_Tratamiento_desigualdad==1] <- 3

w02c$treat <- factor(w02c$treat,levels = c(1,2,3),labels = c("control","pobreza","desiguald"))

w02c <- w02c %>% rename(perc_effort_w2=meritv03_perc_effort,
                        perc_talent_w2=meritv03_perc_talent,
                        perc_wpart_w2 =meritv03_perc_wpart,
                        perc_netw_w2  =meritv03_perc_netw,
                        pref_effort_w2=meritv03_pref_effort,
                        pref_talent_w2=meritv03_pref_talent,
                        pref_wpart_w2 =meritv03_pref_wpart,
                        pref_netw_w2  =meritv03_pref_netw)

w02c <- w02c %>% select(perc_effort_w2,perc_talent_w2,perc_wpart_w2,perc_netw_w2,
                        pref_effort_w2,pref_talent_w2,pref_wpart_w2,pref_netw_w2,
                        sexo_w2=sexo,edad_w2=edad,edcep_w2=edcep, treat, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w02c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
w03c <- w03b

w03c <- w03c %>% rename(perc_effort_w3=meritv03_perc_effort,
                        perc_talent_w3=meritv03_perc_talent,
                        perc_wpart_w3 =meritv03_perc_wpart,
                        perc_netw_w3  =meritv03_perc_netw,
                        pref_effort_w3=meritv03_pref_effort,
                        pref_talent_w3=meritv03_pref_talent,
                        pref_wpart_w3 =meritv03_pref_wpart,
                        pref_netw_w3  =meritv03_pref_netw)
w03c <- w03c %>% select(perc_effort_w3,perc_talent_w3,perc_wpart_w3,perc_netw_w3,
                        pref_effort_w3,pref_talent_w3,pref_wpart_w3,pref_netw_w3,
                        sexo_w3=sexo,edad_w3=edad,edcep_w3=edcep, ID)

#-----------------------------------------------------------------------#
print(dfSummary(w03c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
library(datasets)
library(data.table)

wide <- setDT(wide02)

long01<- melt(wide,variable.name = "wave",
              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
                                       "^sexo_","^edad_","^edcep_"),
              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                             "pref_effort","pref_talent","pref_wpart","pref_netw",
                             "sexo","edad","edcep"))

```

>>>>

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_prep-data-A.Rmd",output_format = "html_document",output_dir = ".")
```

@@

```{r}
dat04 <- w01 %>% filter(Intro==1) %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03_p"),
         starts_with("FL_21_DO"))
dat04$grupo <- NA
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
dat04 <- dat04 %>% select(starts_with(match = "perc_"),starts_with(match = "pref_"),grupo) %>% na.omit()
```

## Translation of variable labels and value labels.
```{r}
label(dat04$grupo) <- "This variable classifies the interviewees according to the order in which the indicators are shown within the scale. There are three orders  of items on the scale. In the first order (group 1), questions of the same factor are then presented to them, in the second order (group 2) they were separated and in the third order (group 3) at random."
dat04$perc_effort <- set_labels(dat04$perc_effort,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they manage to get bigger
rewards that those who strive
less."
dat04$perc_talent <- set_labels(dat04$perc_talent,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they manage to obtain
greater rewards than those who possess
less talent."
dat04$perc_wpart <- set_labels(dat04$perc_wpart,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have rich parents manage to get out
ahead."
dat04$perc_netw <- set_labels(dat04$perc_netw,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$perc_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have good contacts they manage to get out
ahead."
dat04$pref_effort <- set_labels(dat04$pref_effort,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they should get
greater rewards than those who
they try less."
dat04$pref_talent <- set_labels(dat04$pref_talent,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they should get
greater rewards than those who possess
less talent."
dat04$pref_wpart <- set_labels(dat04$pref_wpart,  labels = c("strongly disagree" = 1, "disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "totally agree" = 5))
label(dat04$pref_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Is
well that those who have good
contacts get ahead."
dat04$pref_netw <- set_labels(dat04$pref_netw,  labels = c("strongly disagree", "disagreement", "Neither agree nor disagree","Agree", "totally agree"))
label(dat04$pref_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Is
well that those who have good
contacts get ahead."
```

@@

```{r}
dat01 <- dat04 %>% filter(grupo==1) %>% select(-grupo) %>%  na.omit() 
```

@@

```{r}
dat03 <- dat04 %>% filter(grupo==3) %>% select(-grupo) %>%  na.omit()
```

@@

Add tags wave 1
```{r }
label(w01$Intro) <- "If you wish to participate, select the alternative I ACCEPT take part in this investigation. If you do not want to participate in this study, press the alternative I NOT ACCEPT take part in this investigation."
w01$Intro <- set_labels(w01$Intro,  labels = c("I ACCEPT take part in this investigation","I NOT ACCEPT take part in this investigation."))
```

@@

```{r}
w01c <- w01b
w01c$grupo <- NA
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
w01c$perc_effort_w1 <- rowSums(w01c[,c(matches(match = "perc_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_talent_w1 <- rowSums(w01c[,c(matches(match = "perc_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_wpart_w1  <- rowSums(w01c[,c(matches(match = "perc_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$perc_netw_w1   <- rowSums(w01c[,c(matches(match = "perc_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_effort_w1 <- rowSums(w01c[,c(matches(match = "pref_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_talent_w1 <- rowSums(w01c[,c(matches(match = "pref_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_wpart_w1  <- rowSums(w01c[,c(matches(match = "pref_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_netw_w1   <- rowSums(w01c[,c(matches(match = "pref_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c[w01c==0] <- NA
w01c <- w01c %>% select(grupo,
                        perc_effort_w1,perc_talent_w1,perc_wpart_w1,perc_netw_w1,
                        pref_effort_w1,pref_talent_w1,pref_wpart_w1,pref_netw_w1,
                        sexo_w1=sexo,edad_w1=edad,edcep_w1=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w01c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

Add tags wave 2
```{r }
label(w02$Intro) <- "If you wish to participate, select the alternative I ACCEPT take part in this investigation. If you do not want to participate in this study, press the alternative I NOT ACCEPT take part in this investigation."
w02$Intro <- set_labels(w02$Intro,  labels = c("I ACCEPT take part in this investigation","I NOT ACCEPT take part in this investigation."))
```

@@

Delete those who do not accept and Delete those who do not accept
```{r}
w02b <- w02 %>% filter(Intro==1, Finished==1) %>% as.data.frame()
w02b$ID <- stringr::str_split_fixed(w02b$ticket, "_", 4)[,1]
```

@@

```{r}
w02c <- w02b
w02c$treat <- NA
w02c$treat[w02c$FL_6_DO_Control==1] <- 1
w02c$treat[w02c$FL_6_DO_Tratamiento==1] <- 2
w02c$treat[w02c$FL_6_DO_Tratamiento_desigualdad==1] <- 3
w02c$treat <- factor(w02c$treat,levels = c(1,2,3),labels = c("control","pobreza","desiguald"))
w02c <- w02c %>% rename(perc_effort_w2=meritv03_perc_effort,
                        perc_talent_w2=meritv03_perc_talent,
                        perc_wpart_w2 =meritv03_perc_wpart,
                        perc_netw_w2  =meritv03_perc_netw,
                        pref_effort_w2=meritv03_pref_effort,
                        pref_talent_w2=meritv03_pref_talent,
                        pref_wpart_w2 =meritv03_pref_wpart,
                        pref_netw_w2  =meritv03_pref_netw)
w02c <- w02c %>% select(perc_effort_w2,perc_talent_w2,perc_wpart_w2,perc_netw_w2,
                        pref_effort_w2,pref_talent_w2,pref_wpart_w2,pref_netw_w2,
                        sexo_w2=sexo,edad_w2=edad,edcep_w2=edcep, treat, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w02c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
w03c <- w03b
w03c <- w03c %>% rename(perc_effort_w3=meritv03_perc_effort,
                        perc_talent_w3=meritv03_perc_talent,
                        perc_wpart_w3 =meritv03_perc_wpart,
                        perc_netw_w3  =meritv03_perc_netw,
                        pref_effort_w3=meritv03_pref_effort,
                        pref_talent_w3=meritv03_pref_talent,
                        pref_wpart_w3 =meritv03_pref_wpart,
                        pref_netw_w3  =meritv03_pref_netw)
w03c <- w03c %>% select(perc_effort_w3,perc_talent_w3,perc_wpart_w3,perc_netw_w3,
                        pref_effort_w3,pref_talent_w3,pref_wpart_w3,pref_netw_w3,
                        sexo_w3=sexo,edad_w3=edad,edcep_w3=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w03c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
library(datasets)
library(data.table)
wide <- setDT(wide02)
long01<- melt(wide,variable.name = "wave",
              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
                                       "^sexo_","^edad_","^edcep_"),
              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                             "pref_effort","pref_talent","pref_wpart","pref_netw",
                             "sexo","edad","edcep"))
```
